Model

### 2019-04-29 stats/model.Rmd
model pred with age
update model

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
#sem_know_model <- readRDS("../saves/sem_know_model.rds")
```

@@

ggplot(global_params, aes(x = value))+#, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~token, scales = 'free')+
  theme_few()
```

>>>>

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
sem_know_model <- readRDS("../saves/sem_know_model.rds")
```

@@

ggplot(global_params, aes(x = value))#, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~token, scales = 'free')+
  theme_few()
```
